---
title: "Brownlows Bets"
author: "Brooke De La Torre"
date: "Year 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)
```


<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

We will be showing the profit that Brownlow made from the bet he made with students regarding whether at least 2 people had birthdays on the same date.

# Methods  


<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 637 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->

we will solve this problem by resampling. we will set up days of the year, take a random sample of 35, and see if two or more have the same birthday. 

```{r}
daysYEAR=1:365
bDAYS=sample(daysYEAR,35,replace=TRUE)
length(unique(bDAYS))
```
```{r}
results=vector("numeric")
for(j in 1:1000){
bank=0
for(i in 1:637){
  class = sample(daysYEAR,35,replace=TRUE)
  n=length(unique(class))
  if(n == 35)bank=bank-2
  else bank=bank+1
}
results[j]=bank
}
hist(results)
```


# Profit Estimate

```{r}
favstats(results)
```
the expected amount of money is `r mean(results)`
# Confidence interval of Brownlows earning
# 95% Confidence interval
```{r}
results=vector("numeric")
for(j in 1:1000){
bank=0
for(i in 1:637){
  class = sample(daysYEAR,35,replace=TRUE)
  n=length(unique(class))
  if(n == 35)bank=bank-2
  else bank=bank+1
}
results[j]=bank
}
sortRESULTS=sort(results)
lcl=sortRESULTS[25]
ucl=sortRESULTS[975]
```

lower confidence limit= `r lcl`
upper confidence limit= `r ucl`


# fair odds pay off

```{r}
results=vector("numeric")
for(j in 1:1000){
bank=0
for(i in 1:637){
  class = sample(daysYEAR,35,replace=TRUE)
  n=length(unique(class))
  if(n == 35)bank=bank-5
  else bank=bank+1
}
results[j]=bank
}
hist(results)
```
The amount that Brownlow would have to pay to make this a fair bet is $5

# number of students for a fair bet
  
```{r}
results=vector("numeric")
for(j in 1:1000){
bank=0
for(i in 1:637){
  class = sample(daysYEAR,28,replace=TRUE)
  n=length(unique(class))
  if(n == 28)bank=bank-2
  else bank=bank+1
}
results[j]=bank
}
hist(results)
```
The amount of students that would have to partcipate for it to be a fair bet is 28.

<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows betting profits!-->

  
<!--Explain and display your method of coming up with a 95% confidence interval of  professor Brownlows winnings (or losings)-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->

The amount that Brownlow would have to pay to make this a fair bet meaning that the profit would balance at 0 is $5.The amount of students that would have to partcipate for it to be a fair bet is 28.The mean expected amount he could make is  281.731. 

